Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-09-03 data/result/Article/Latex/Article.tex
.

A summary of values collected for each quality indicator and instance is presented in Table II. The distributions of these values are shown in the box-plots presented in Figure I. Data for NSGAII is shown in the form of mean $\pm$ standard deviation over the 50 cycles. Data for OMS is shown as a single value, since each OMS produced a single Pareto front for each instance. I$_{HV}$ and I$_{GD}$ for CPM on instances PARM and PSOA are not calculated because the OMS produced a Pareto front comprised of a single vertex, leading to undefined I$_{GD}$ and I$_{HV}$. Bold face OMS values were found significantly different from NSGAII using Bonferroni-adjusted Wilcoxon-Mann-Whitney inference tests at 95\% significance level. Bold face NSGAII values were found significantly different from all OMS using the same inference test.

>>>>

A summary of values collected for each quality indicator and instance is presented in Table II. The distributions of these values are shown in the box-plots presented in Figure I. Data for NSGAII is shown in the form of mean $\pm$ standard deviation over the 50 cycles. Data for OMS is shown as a single value because each OMS produced one Pareto front for each instance. I$_{HV}$ and I$_{GD}$ for CPM on instances ACAD, PSOA, and PARM are not calculated because the OMS produced a Pareto front comprised of only two vertices, leading to undefined I$_{GD}$ and I$_{HV}$. Bold face values were found significantly different in the comparison between NSGAII and all OMS using Bonferroni-adjusted Wilcoxon-Mann-Whitney inference tests at 95\% significance level.
